A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-31 4_method.tex
move beading conflicts section down to beading section
disable transition_placement figure

A transition with length $t(n)$ will be placed somewhere covering the anchor position.
We determine the distance between the anchor $v$ and the lower transition end $v_0$ proportial to the positioning of the transition relative to the preferred distances: 
$$d_-^\text{transition}(v) =  t(n) (b^{-1}(n) - p(n) ) / (p(n+1) - p(n))$$
See \cref{transition_placement}.
For the other end we have $d_+^\text{transition}(v) = t(n) - d_-^\text{transition}(v)$.
That way the transitions never overlap locations with preferred bead count.

@@

\begin{figure}
\centering
\includegraphics[width=.3\columnwidth]{sources/method/transition_location_precise.pdf}
\caption{
Transition placement.
The anchor position within the transition length is proportional to the transition location within the range between two distances with preferred length. 
}
\label{transition_placement}
\end{figure}

\todo{TODO: implement this! }
\todo{Compute beading propagation after initial $B^*$ assignment, but before transitioning}
\todo{Explain beading propagation before transitioning}

@@

>>>>

A transition with length $t(n)$ will be placed somewhere covering the anchor position.
We determine the distance between the anchor $v$ and the lower transition end $v_0$ proportial to the positioning of the transition relative to the preferred distances: 
$$d_-^\text{transition}(v) =  t(n) (b^{-1}(n) - p(n) ) / (p(n+1) - p(n))$$
%See \cref{transition_placement}.
For the other end we have $d_+^\text{transition}(v) = t(n) - d_-^\text{transition}(v)$.
That way the transitions never overlap locations with preferred bead count.

@@

\iffalse
\begin{figure}
\centering
\includegraphics[width=.3\columnwidth]{sources/method/transition_location_precise.pdf}
\caption{
Transition placement.
The anchor position within the transition length is proportional to the transition location within the range between two distances with preferred length. 
}
\label{transition_placement}
\end{figure}
\fi

@@

\todo{Compute beading propagation after initial $B^*$ assignment, but before transitioning}
\todo{Explain beading propagation before transitioning}
